Proposition of a New Experiment to Better Understand the Relation Between Typicality and Prototypes

### 2022-06-04 paper.tex
Finished

\documentclass[conference]{IEEEtran}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolour}
\usepackage[backend=biber, sorting=none]{biblatex}
\usepackage{lipsum}
\usepackage{url}
\usepackage{subcaption}
\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
\addbibresource{bibliography.bib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

		\noindent The possible applications of this experiment are widely ranged. First of all, this experiment could help neuroscientists understand how the knowledge is 
		organized in the brain. By doing so, there is the possibility to increase the knowledge about the brain and how it works. Moreover, it's possible to confront 
		the way that a person with cognitive disorders or, more generally, some kind of mental disorder related to knowledge with the results of people without 
		any disorder, trying to understand if the way that knowledge is handled in the brain is somehow similar or completely different. Lastly, this experiment can 
		also help to understand if knowledge is encoded in a similar way in artificial and biological neural systems.

@@

			\noindent Typicality is one of the key concepts that will be used in this paper, so it's fundamental that it's defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, in this paper, defined  a measure of how representative an example is of their category and 
			of the other members of the same category.

		\subsection{Feature extraction}

			\noindent Feature extraction is a topic widely studied. 
			This topic has numerous different applications. 
			One of its goals is to reduce the amount of computational power needed for image processing. 
			There are various techniques to extract meaningful features from images. 
			Some of them are very common and very easy to implement. 
			These are, for example, edge extraction or shape analysis. 
			Other possibilities, more advanced, involve neural networks.\\

@@

					One of the first feature extraction methods implemented in image processing is edge detection.				
					In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
					These are usually divided into two groups, gradient-based and Gaussian-based. 
					Some examples are the Sobel operator and the Canny edge detector. 
					Each of the methods has pros and cons. 
					It's the user's job to find the most appropriate for its goal~\cite{owotogbe2019edge}.\\

@@

							The Fourier transform is commonly used for shape analysis. 
							The Fourier transformed coefficient form the Fourier descriptors. 
							These descriptors represent the shape in a frequency domain, with the low frequencies symbolizing the general shape and the high frequencies symbolizing details of the shape. 
							Since the transformation usually generates many parameters, only a subset is considered.

@@

					A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{felzenszwalb2005representation}. For the goal of the experiment proposed here, some deformable shape 
					detection techniques can be useful. \\
					The technique proposed strongly relies on the triangulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
					%The resulting approximation is as precise as the user decides, meaning that it's very flexible for the representation of shapes. 
					%In particular, in the paper the triangulation was done with a technique called constrained Delaunay triangulation (CDT), because of its tight relation with the medial axis transform. 
					The author also make use of the properties of chordal graphs and k-trees.\\
					The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
					possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since depending on the formulation of the energy function the costs 
					can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually requires an initialization near to the correct solution, 
					although this is not required for the algorithm presented in this paper. 
					For the implementation of the algorithm itself, a techniques called non-serial dynamic programming was the key factor. In fact, using the order of perfect elimination (property of the every triangulated 
					simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
					update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
					The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
					energy cost, which corresponds to the best template match.

					\begin{figure}[!ht]
						\centerline{\includegraphics[height=0.4\textheight]{imgs/delaunay.jpg}}
						\caption{Example of delaunay triangulation, the type of triangulation at the base of Felzenszwalb's paper}
						\label{fig:3}
					\end{figure}

@@

					\noindent In 2019, there is another paper, written by Varshni et al. that proposes another method~\cite{varshni2019pneumonia}. This paper has the objective to classify images suing CNNs to understand if a patient 
					has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
					In this paper's results it's reported that the best model architecture is DenseNet-169. This kind of neural network, called Dense Nets, overcomes the problem of gradient vanishing. The model used in 
					particular for the work of this paper had 4 dense blocks and 3 transition layers. Then there is a classification layer.

@@

					Although there exists techniques that can extract features from hyperspectral images, this kind of images are created to capture the entire spectrum. This fact means that these images can capture 
					more information then what the human eye can. techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent 
					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it's probably more meaningful to use normal 
					images than these ones.

@@

				\subsubsection{Convolutional Neural Network (CNN)}

					Convolutional neural networks are not an extremely recent type of neural network, especially if we consider that LeNet-5 was created in 1998. Scientists have dealt with CNNs for some years. Now, as of 2022, 
					CNNs are mostly used to deal with images.\\
					In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs~\cite{wu2017introduction}. These networks use mostly three kind of layers: Dense layers (which are fully connected layers), 
					convolution layers and pooling layers. In the following, there will be a short description of each kind of layer. 
					\begin{itemize}

@@

				\subsubsection{Siamese Neural Network}

					Siamese neural networks, also called twin networks, are a more recent advance in computer science. These neural networks have a different structure from convolutional neural networks. The 
					structure of siamese neural networks is peculiar. In fact, there are two identical networks, called embedding networks, that process different inputs and, after that, 
					merge in a single layer that measures the similarity between 
					the two outputs of the two networks. The siamese neural networks have a different application compared to CNNs, in fact twin networks are mainly used to measure similarity of two objects. 
					In the case of this paper, the siamese neural networks are used for image matching. This is not the first time that siamese networks are used for image matching, as proved by a paper written in 2016 by 
					Melekhov et al.~\cite{melekhov2016siamese}, but with a little difference in the objective of the matching. The objective of the paper was to learn a general similarity for image retrieval, while on the case of this 
					paper, the objective is to find a similarity measure with a prototype.

@@

					% Training with triplets (?)

@@

				In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017~\cite{appalaraju2017image}. In this work they explore the possibility to 
				find a similarity measure for image retrieval. To achieve this goal, they implemented a siamese neural network that uses two identical multi-scale CNNs that share weights. The ouput of the 
				network is binary, being $1$ the label to predict in case of negative examples and $0$ the label to predict in case of positive example. The loss function used in this work is a contrastive loss. This paper 
				then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspired by curriculum learning, that helps reducing the training time. \\
				This is not the only work that uses neural networks to learn similarity, in fact there are also other application fields for similarity study. One of them is healthcare, as shown in a paper by Suo et al., written in 
				2017, that introduces a model used to make personalized prediction of diseases for patients, basing the prediction on a similarity related method, learned using CNNs~\cite{8217759}. In this paper, before 
				learning the actual similarity measure, the authors processed the input through a CNN and performed a step they call ``Time fusion''. This step let them incorporate the time information and 
				weight differently eventual symptoms based on their temporal distance from the onset of the disease. Only after this step the authors proceeded to learn a similarity metric, basing the learning 
				on CNNs.\\
				Another paper, written by Chopra et al. in 2005, used a method similar to the one written by Appalaraju. In this work, the authors used a siamese architecture to learn a similarity metric and applied it 
				in the field of face verification~\cite{chopra2005learning}.\\
				More interestingly, there are also other papers, in particular a paper by Attarian et al. written in 2020 uses $VGG16$. This paper's goal is to use this CNN to predict human similarity 
				judgments~\cite{attarian2020transforming}. Using $VGG16$, the authors were able to achieve good results, with over 90\% in validation accuracy.

@@

			\noindent Since the proposed experiment uses neural networks, there is the need to have a lot of data. In this particular case, there is the need to gather many images. There are some image dataset, intended for computer 
			vision~\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help. Some of the dataset reported there are quite famous, like ImageNet or Google's Open Images. The 
			best for this kind of work, though, is to have a dataset that bases every image on the same ``macro-category'', like for example a dataset made of images of birds. Even though this is the ideal case,
			most of the dataset that are used for computer vision contain more than one single category. For example, ImageNet, which is one of the most famous image datasets, contains more than 1 million images that are divided 
			into 1000 classes. Generally, it's possible to use these datasets, which have different macro categories by filtering the input images based on the macro category the experiment is based on.

@@

			Another possibility to gather data, it's to ask people to list a certain number of objects or all the objects they can think about of the decided category. For example, let's assume the macro category decided 
			is ``birds''. It's possible to collect enough data by asking people to list a the first few examples of birds, using a predefined number. Moreover, it's possible to use a variant of this procedure and ask people 
			to list all the examples of birds that they can think of. These two variants of the same data collection approach are both possible and come with some advantages and disadvantages when compared to the other 
			method described in \ref{sec:typval}. % In case this type of data collection is used, the values of typicality should be also a question that asks the subjects to describe all the features that birds have in common 
			% with each other. This step will then be used for prototype construction.

@@

			The two presented methods proposed for data collection are very different. Both of these have their own pros and cons. The first method can help in having a typicality value for every image collected in the dataset, 
			while the second does not. The large number of images that should be used, though, it's not feasible to ask the subjects to rate the typicality value of all the images of the dataset. In fact, it's very likely 
			that a subject that has to rate the typicality of a large number of images will be tired after a certain number of images, polluting the results of the survey. A possible solution to this problem is to 
			divide the survey so that subjects have to rate the typicality of a limited number of images. This method would result in a lower amount of data, but at the same time, a more precise amount of data. Another 
			problem with this method it's that it has a possible bias. In fact, if a person sees a bird, for example a swan, or a duck, and is asked to rate its typicality, most likely will rate it in the higher part 
			of the scale, while if asked to list a certain number of birds it's more likely that it's not present than that it's present.\\
			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject didn't think of. 
			Recalling the previous example with the swan, if a person does not think of the swan, it won't be present in the list created by the subject. This could result in a lower bias, but it comes at the cost 
			of having to interview more people and, most likely, not having enough data for some of the examples. In this approach, the more a bird is typical, the more it appears in the lists and in higher positions. 
			There is an example in the appendix. Even though this method has the advantage of having less bias, has a  great drawback. That is, in particular, the fact that the prototype construction is very difficult.\\
			In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two 
			methods and decide which one is more convenient.
			As alternative, it's possible to try both the methods and see which one gives better results. In this way, both the possibilities will be used and there is the possibility to see which one is better in 
			terms of performance.

@@

		\noindent While collecting the needed data with the survey, it's possible to begin the feature extraction procedure. There are various possibilities for this step, as shown in the Section dedicated to feature extraction background. 
		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient. Since feature extraction has already been described in the paper, this section will 
		present a discussion about the results of the presented methods' results. The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
		In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process. For example, in edge extraction, humans have no difficulty in recognizing if the 
		edge extracted is correct or not seeing the original image. For example, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left, 
		while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
		Moreover, classical and machine learning features can give different weights to different features. 
		In fact, classical methods rely mostly on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works. An empirical confirmation of this fact 
		can be that if a person asks to another person to describe, for example, a common kingfisher, the person that should describe the bird will, most likely, start describing the dimension, the shape, and only 
		later the colour. Machine learning techniques, on the other hand, could give a very high importance to the fact that the bird is mainly blue and red, if they have access to the colour information. Due to the fact that 
		the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to 
		shape-related features.	\\
		If the data collection method chosen is the one that asks people to list the objects of the category, the feature extraction can happen in two possible ways. The first way is to use the data collected for 
		typicality judgments and collect also images of the birds that appear in the results. After collecting enough images, the feature extraction process can proceed as described earlier and use either  
		classical or machine-learning-based feature extraction methods. Although this is a possibility, there could be an alternative. The alternative seems interesting because it can be adapted to rely only on features 
		that humans identify as important. To do so, the survey should include a question that asks the subjects to list all the characteristics that the objects of the given macro category have in common. In this case, 
		the features are not strictly extracted by the dataset, but are listed by the subjects that take part in the survey. By doing so, the experiment takes into account, in the prototype, only the features that 
		human have listed, so only the features that are considered important by humans themselves. Although it's theoretically possible, this procedure will result in numerous complication in prototype construction.

@@

		\subsection{Classical feature extraction techniques}

			\noindent In case classical feature extraction techniques were used, the goal of this activity is to build an image that presents in itself a ``prototype'' of the object. For example, a prototype of a bird, could be 
			an imaginary bird with a shape that it's obtained with a weighted average of the shapes of all the birds in the image. For example, since a birds like sparrows and swallows are perceived as more 
			typical than ostriches and penguins the prototype should resemble more swallows and sparrows than ostriches and penguins. To do so, the key factor is performing numerous analyses on various 
			different subjects, until there are enough data to have a statistical value.

			\begin{figure*}[!t]
				\centering
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
				\end{subfigure}
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[height=0.4\textheight]{imgs/penguin_edges.jpg}}
				\end{subfigure}
				\caption{Edge extraction of swallow and penguin}
				\label{fig:7}
			\end{figure*}

		\noindent In Figure \ref{fig:7} there is an example of the edges of two different birds. Although both of the subjects of the original 
		subjects are birds, one is much more typical than the other one. In this case, the prototype should try to match more the swallow edge than the penguin edge. A way to do so could make use deformable 
		template matching. Matching a shape with a template could be useful to find a weighted average between the two shapes. In this way, the resulting shape takes into account both the original edges while 
		giving priority to the one more typical.
		This procedure should be applied for both shape features and colour features, so that all the features that can be extracted from the prototype image resemble the weighted average of all the feature from 
		the original images.

		\subsection{Machine learning feature extraction techniques}

			\noindent In case machine learning feature extraction techniques were used, it's conceptually and practically easier to compute the average features. In fact, the features extracted by machine learning techniques are 
			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors. 
			%Allungare (?)

		\subsection{Other survey method}

			%Diificile, da pensare bene.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolour}
\usepackage[backend=biber, sorting=none]{biblatex}
\usepackage{url}
\usepackage{subcaption}
\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
\addbibresource{bibliography.bib}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

		\noindent The possible applications of this experiment are widely ranged. First of all, this experiment could help neuroscientists understand how the knowledge is 
		organized in the brain. By doing so, there is the possibility to increase the knowledge about the brain and how it works. Moreover, it's possible to confront 
		the way that a person with cognitive disorders or, more generally, some kind of mental disorder related to knowledge with the results of people without 
		any disorder, trying to understand if the way that knowledge is organized in the brain is similar or completely different. Lastly, this experiment can 
		also help to understand if knowledge is encoded in a similar way in artificial and biological neural systems.

@@

			\noindent Typicality is one of the key concepts that will be used in this paper, so it's fundamental that it's defined. In a paper by Dieciuc and Folstein~\cite{dieciuc2019typicality},
			the authors, before defining typicality, state that every object in the environment is unique. Then, they state that in categorizing objects, we put them in the same category 
			despite their difference, minimizing the differences and maximizing the similarities. So typicality is, as defined in this paper, a measure of how representative 
			an example is of their category and of the other members of the same category.

		\subsection{Feature extraction\label{sec:bfe}}

			\noindent Feature extraction is a topic widely studied. 
			This topic has numerous applications. 
			One of its goals is to reduce the amount of computational power needed for image processing. 
			There are various techniques to extract meaningful features from images. 
			Some of them are very common and very easy to implement. 
			These are, for example, edge extraction or shape analysis. 
			Other possibilities, more advanced, involve neural networks.\\

@@

					One of the first feature extraction methods implemented in image processing is edge detection.				
					In 2019, a paper by Owotogbe presented a review of edge detection techniques. 
					These are usually divided into two groups, gradient-based and Gaussian-based. 
					Some examples are the Sobel operator and the Canny edge detector. 
					Each algorithm has its own peculiarities and it's the user's job to find 
					the most appropriate for its goal~\cite{owotogbe2019edge}.\\

@@

							The Fourier transform is commonly used for shape analysis. 
							The transformed coefficient are called the Fourier descriptors.
							These descriptors represent the shape in a frequency domain, with the low frequencies symbolizing the general shape and the high frequencies symbolizing details of the shape. 
							Since the transformation usually generates many parameters, only a subset is considered.

@@

					A more sophisticated technique than the ones listed before is shape analysis. Deformable shape analysis, in particular, can be useful to extract features from an image.\\
					In 2005, Felzenszwalb wrote a paper that focuses on representation and detection of deformable shapes~\cite{felzenszwalb2005representation}. For the goal of the experiment proposed here, some deformable shape 
					detection techniques can be useful. \\
					The technique proposed strongly relies on the triangulated polygon representation. This type of representation lets approximate every 2D shape without holes using a representation based on triangles. 
					The author also make use of the properties of chordal graphs and k-trees.\\
					The technique described in this paper falls under the category of deformable template matching. One of the components of the method is the energy function, a function that associates a cost with every 
					possible transformation. The objective is to find the transformation with the lowest possible cost. This component is very flexible, since, depending on the formulation of the energy function, the costs 
					can be tuned even for individual triangles. Moreover, it is also possible to integrate learning techniques to learn deformation parameters.
					Since the possible non-rigid transformations of a template are numerous, this kind of techniques usually require an initialization near to the correct solution, 
					although this is not required for the algorithm presented in this paper. 
					For the implementation of the algorithm itself, a technique called non-serial dynamic programming was the key factor. In fact, using the order of perfect elimination (property of the every triangulated 
					simple polygon), the algorithm computes the optimal position of every vertex with respect to the other vertices. Once the algorithm solves for the last vertex, it can 
					update all the others as in typical dynamic programming and obtain the optimal location for every vertex.\\
					The learning of the parameters can be seen as looking for the location with the highest. The matching problem is then fed to a statistical framework that computes the configuration minimizing the 
					energy cost, which corresponds to the best template match.

					\begin{figure}[!ht]
						\centerline{\includegraphics[height=0.4\textheight]{imgs/delaunay.jpg}}
						\caption{Example of Delaunay triangulation, the type of triangulation at the base of Felzenszwalb's paper}
						\label{fig:3}
					\end{figure}

@@

					\noindent In 2019, there is another paper, written by Varshni et al. that proposes another method~\cite{varshni2019pneumonia}. This paper has the objective to classify images using CNNs to understand if a patient 
					has pneumonia or not. After the preprocessing, in which the authors just resized the images, there is the feature extraction process. For this step, the authors used different pretrained models.
					In this paper's results it's reported that the best model architecture is DenseNet-169. This kind of neural network, called Dense Nets, overcomes the problem of gradient vanishing. The model used in 
					particular for the work of this paper had 4 dense blocks and 3 transition layers. Then there is a classification layer.

@@

					Although there exists techniques that can extract features from hyperspectral images, this kind of images are created to capture the entire spectrum. This fact means that these images can capture 
					more information then what the human eye can. The techniques involve, in the majority of the cases, learning of some form, especially in form of neural networks, in particular convolutional recurrent 
					networks, as seen in a paper by Hu et al.~\cite{hu2020spatial} and in a paper by Rasti et al.~\cite{rasti2020feature}. For the reasons just said, it's probably more meaningful to use normal 
					images than these ones.

@@

				\subsubsection{Convolutional Neural Networks (CNN)}

					Convolutional neural networks are not an extremely recent type of neural network, especially if we consider that LeNet-5 was created in 1998. Scientists have dealt with CNNs for some years. Now, as of 2022, 
					CNNs are mostly used to deal with images.\\
					In 2017, Wu wrote a paper that had the purpose to serve as an introduction to CNNs~\cite{wu2017introduction}. These networks use mostly three kind of layers: Dense layers (which are fully connected layers), 
					Convolutional layers and Pooling layers. In the following, there will be a short description of each kind of layer. 
					\begin{itemize}

@@

				\subsubsection{Siamese Neural Networks}

					Siamese neural networks, also called twin networks, are a more recent advance in computer science. These neural networks have a different structure from convolutional neural networks. The 
					structure of siamese neural networks is peculiar. In fact, there are two identical networks, called embedding networks, that process different inputs and, after that, 
					they merge in a single layer that measures the similarity between 
					the two outputs of the two networks. The siamese neural networks have a different application compared to CNNs, in fact twin networks are mainly used to measure similarity of two objects. 
					In the case of this paper, the siamese neural networks are used for image matching. This is not the first time that siamese networks are used for image matching, as shown in a paper written in 2016 by 
					Melekhov et al.~\cite{melekhov2016siamese}, but with a little difference in the objective of the matching. The objective of the paper was to learn a general similarity for image retrieval, while on the case of this 
					paper, the objective is to find a similarity measure with a prototype.

@@

@@

				\noindent In the past there have been some works regarding image similarity, like for example the one presented by Appalaraju and Chaoji in 2017~\cite{appalaraju2017image}. In this work they explore the possibility to 
				find a similarity measure for image retrieval. To achieve this goal, they implemented a siamese neural network that uses two identical multi-scale CNNs that share weights. The ouput of the 
				network is binary, being $1$ the label to predict in case of negative examples and $0$ the label to predict in case of positive example. The loss function used in this work is a contrastive loss. This paper 
				then proceeds to explain a technique called Online Pair Mining Strategy (OPMS), inspired by curriculum learning, that helps reducing the training time. \\
				This is not the only work that uses neural networks to learn similarity, in fact there are also other application fields for similarity study. One of them is healthcare, as shown in a paper by Suo et al., written in 
				2017, that introduces a model used to make personalized prediction of diseases for patients, basing the prediction on a similarity related method, learned using CNNs~\cite{8217759}. In this paper, before 
				learning the actual similarity measure, the authors processed the input through a CNN and performed a step they call ``Time fusion''. This step let them incorporate the time information and 
				weight differently eventual symptoms based on their temporal distance from the first appearance of the disease. Only after this step the authors proceeded to learn a similarity metric, basing the learning 
				on CNNs.\\
				Another paper, written by Chopra et al. in 2005, used a method similar to the one written by Appalaraju. In this work, the authors used a siamese architecture to learn a similarity metric and applied it 
				in the field of face verification~\cite{chopra2005learning}.\\
				More interestingly, there are also other papers, in particular a paper by Attarian et al. written in 2020 uses $VGG16$. This paper's goal is to use this CNN to predict human similarity 
				judgments~\cite{attarian2020transforming}. Using $VGG16$, the authors were able to achieve good results, with over 90\% in validation accuracy.

@@

			\noindent Since the proposed experiment uses neural networks, there is the need to have a lot of data. In this particular case, there is the need to gather many images. There are some image dataset, intended for computer 
			vision\footnote{\url{https://imerit.net/blog/22-free-image-datasets-for-computer-vision-all-pbm/}}, that could help. Some of the dataset reported there are quite famous, like ImageNet or Google's Open Images. The 
			best for this kind of work, though, is to have a dataset of which every image is part of the same ``macro-category'', like for example a dataset made of images of birds. Even though this is the ideal case,
			most of the dataset that are used for computer vision contain more than one single category. For example, ImageNet, which is one of the most famous image datasets, contains more than 1 million images that are divided 
			into 1000 classes. Generally, it's possible to use these datasets, which have different macro categories by filtering the input images based on the macro category the experiment is based on.

@@

			\noindent Another possibility to gather data, it's to ask people to list a certain number of objects or all the objects the subjects can think about of the decided category. For example, let's assume the macro category decided 
			is ``birds''. It's possible to collect enough data by asking people to list the first few examples of birds, using a predefined number. Moreover, it's possible to use a variant of this procedure and ask people 
			to list all the examples of birds that they can think of. These two variants of the same data collection approach are both possible and come with some advantages and disadvantages when compared to the other 
			method described in \ref{sec:typval}.

		\subsection{Test of the second data collection method}

		\noindent To test the method of data collection described in \ref{sec:patv}, I collected the results of a small survey in which there were 10 questions, each asking to give the name of a bird. The number of 
		people that answered is not big enough to be a statistically relevant group, since the number of the answers is only $14$.

		\begin{figure*}
			\centerline{\includegraphics[width=\linewidth]{imgs/survey_hist.png}}
			\caption{Results of the survey}
			\label{fig:7}
		\end{figure*}

		\noindent In Figure \ref{fig:7} there are the results of the survey. Even though the number of answers was not very big, some problems still emerged.
		\begin{itemize}

				In this case, one of the answers had to be deleted from the answers, since the cited example was not part of the category decided for the survey. In particular, the survey asked for examples of birds, 
				while one of the answers was a mammal. This fact highlights a problem bound to the number of examples the user knows or can think of. In this example, the survey asked for $10$ names of birds,
				which I thought was a reasonable number, but probably some of the subjects that took part to this survey could not think of a $10^{th}$ name, so just put a name of another animal. The solution 
				to this problem is to apply some data cleaning to the answers to filter the examples that, eventually, are in the answers but not part of the given category. An analogue approach can be applied if the 
				subject leaves the answer blank for the same reason.

				This problem is simpler than the previous one to solve, since it just involves the capitalization of the answers. If the survey starts accounting numerous results, it becomes difficult to 
				compute the number of times that a particular example appears in the answers, so, most likely, there will be some automated scripts that compute all the needed statistics. This could be a problem since 
				in most of the programming languages, if not all, words like ``Robin'' and ``robin'' are considered different based on the capitalization. This problem is easily solvable by lowercasing all the 
				answers.

				This problem can be quite challenging to solve. In fact, subjects could make some mistakes when typing the answers, so for example a word like ``robin'' can become ``ribin'' or ``tobin'' for example. 
				Moreover, if more than one letter is wrong, some results like ``rivim'' instead of ``robin'' are possible, especially if the subjects compile the form via mobile devices. To solve this issue, 
				it's possible to use some distance between strings, like for example the Levenshtein distance, which is used to find the distance between two strings. Although this could be a solution,
				it's not guaranteed that the result is correct, so these results should always be checked again to prove they are correct and, most importantly, coherent with the category the survey is based on.

				This problem is very difficult to overcome. There is an example in the histogram reported as results. In the histogram, in fact, it's possible to note that there are both the ``eagle'' and 
				the ``bald eagle'' labels. This means that different subjects can answer with different levels of specificity, since the ``eagle'' label is more general than its counterpart ``bald eagle''. 
				This problem is presented also in an inter-species context, for example the ``Common kingfisher'' represents a single specie, representative of the ``kingfisher'' genus, while, for example, 
				``Flamingo'' represents a family, of which some examples are the greater flamingo and the lesser flamingo, along with other species as well. 
				Even though the problem is very clear, it's not very clear what to do in this case. A possibility is to decide that, in the case of the presented survey, 
				the ``bald eagle'' label should be incorporated in the ``eagle'' 
				label, making sure that all the instances of the most specific one are accounted as instances of the more general one. Another possibility is to keep both of the labels, so that the results of 
				the survey are unaltered. Lastly, it's possible to assume that every label that identifies a group more general than a single specie, like a family or a whole order is referred to the most 
				common specie of that family or order. The only way to know exactly which of these possibilities performs better is conducting some experiments and compare the obtained results.

@@

			\noindent The two presented methods proposed for data collection are very different. Both of these have their own peculiarities. The first method can help in having a typicality value for every image collected in the dataset, 
			while the second does not. Given the large number of images that should be used, though, it's not feasible to ask the subjects to rate the typicality value of all the images of the dataset. In fact, it's very likely 
			that a subject that has to rate the typicality of a large number of images will be tired after a certain number of images, polluting the results of the survey. A possible solution to this problem is to 
			divide the survey so that subjects have to rate the typicality of a limited number of images. This method would result in a lower amount of data, but at the same time, a more precise amount of data. Another 
			problem with this method it's that it has a possible bias. In fact, if a person sees a bird, for example a swan, or a duck, and is asked to rate its typicality, most likely will rate it in the higher part 
			of the scale, while if asked to list a certain number of birds it's more likely that it's not present than that it's present.\\
			On the other hand, the second method gives a possibly lower bias, since there are no images that can influence the subject's mind showing images of examples of the category that the subject didn't think of. 
			Recalling the previous example with the swan, if a person does not think of the swan, it won't be present in the list created by the subject. This could result in a lower bias, but it comes at the cost 
			of having to interview more people and, most likely, not having enough data for some of the examples. In this approach, the more a bird is typical, the more it appears in the lists and in higher positions. 
			There is an example in the appendix. Even though this method has the advantage of having less bias, has a  great drawback. That is, in particular, the fact that the prototype construction is very difficult.\\
			In order to give the proper weight to both the pros and cons and decide which is the best, the best decision is asking for help to a psychologist or a neuroscientist so that both pros and cons of the two 
			methods have the right weight and it's easier to decide which one is more convenient.
			As alternative, it's possible to try both the methods and see which one gives better results. In this way, both the possibilities will be used and there is the possibility to see which one is better in 
			terms of performance.

@@

		\noindent While collecting the needed data with the survey, it's possible to begin the feature extraction procedure. There are various possibilities for this step, as shown in Section \ref{sec:bfe}, which is
		the section dedicated to feature extraction background. 
		It could be interesting to test both classical and machine learning methods, to measure which one is the most efficient. Since feature extraction has already been described in the paper, this section will 
		present a discussion about the results of the presented methods' results. The main difference between the classical and the machine learning feature extraction techniques is human interpretability. 
		In fact, for classical feature extraction techniques, humans have no difficulty in interpreting the result of the process. For example, in edge extraction, humans have no difficulty in recognizing if the 
		edge extracted is correct or not seeing the original image. For example, in Figure \ref{fig:1} no one has any problem to recognize that the figure on the right is the one that draws the edges of the figure on the left, 
		while in Figure \ref{fig:4} there is no clear correlation between the feature and what it means in the image itself.
		Moreover, classical and machine learning features can give different weights to different features. 
		In fact, classical methods rely mostly on features that humans consider important, on the basis of general experience about the world, but also based on the way our brain works. An empirical confirmation of this fact 
		can be that if a person asks to another person to describe, for example, a common kingfisher, the person that should describe the bird will, most likely, start describing the dimension, the shape, and only 
		later the colour. Machine learning techniques, on the other hand, could give a very high importance to the fact that the bird is mainly blue and red, if they have access to the colour information. Due to the fact that 
		the blue colour is not very present in nature, the blue and red couple of colours can be highly characteristic of the common kingfisher, even if humans give, unconsciously and innately, more importance to 
		shape-related features.	\\
		If the data collection method chosen is the one that asks people to list the objects of the category, the feature extraction can happen in two possible ways. The first way is to use the data collected for 
		typicality judgments and collect also images of the examples that appear in the results. After collecting enough images, the feature extraction process can proceed as described earlier and use either  
		classical or machine-learning-based feature extraction methods. Although this is a possibility, there could be an alternative. The alternative seems interesting because it can be adapted to rely only on features 
		that humans identify as important. To do so, the survey should include a question that asks the subjects to list all the characteristics that the objects of the given macro category have in common. In this case, 
		the features are not strictly extracted by the dataset, but are listed by the subjects that take part in the survey. By doing so, the experiment takes into account, in the prototype, only the features that 
		human have listed, so only the features that are considered important by humans themselves. Although it's theoretically possible, this procedure will result in numerous complication in prototype construction.

@@

		\subsection{After classical feature extraction techniques\label{sec:cfet}}

			\noindent In case classical feature extraction techniques were used, the goal of this activity is to build an image that presents in itself a ``prototype'' of the object. For example, a prototype of a bird, could be 
			an imaginary bird with a shape that it's obtained with a weighted average of the shapes of all the birds in the image. For example, since birds like sparrows and swifts are perceived as more 
			typical than ostriches and penguins the prototype should resemble more swifts and sparrows than ostriches and penguins. To do so, the key factor is performing numerous analyses on various 
			different subjects, until there are enough data to have a statistical value.

			\begin{figure*}[!t]
				\centering
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[width=0.9\linewidth]{imgs/swallow_edges.jpg}}
				\end{subfigure}
				\begin{subfigure}[!t]{0.48\linewidth}
					\centerline{\includegraphics[height=0.4\textheight]{imgs/penguin_edges.jpg}}
				\end{subfigure}
				\caption{Edge extraction of swift and penguin}
				\label{fig:8}
			\end{figure*}

		\noindent In Figure \ref{fig:8} there is an example of the edges of two different birds. Although both of the original 
		subjects are birds, one is much more typical than the other one. In this case, the prototype should try to match more the swift edge than the penguin edge. A way to do so could make use deformable 
		template matching. Matching a shape with a template could be useful to find a weighted average between the two shapes. In this way, the resulting shape takes into account both the original edges while 
		giving priority to the one more typical.
		This procedure should be applied for both shape features and colour features, so that all the features that can be extracted from the prototype image resemble the weighted average of all the feature from 
		the original images.

		\subsection{After machine learning feature extraction techniques\label{sec:mlfet}}

			\noindent In case machine learning feature extraction techniques were used, it's conceptually and practically easier to compute the average features. In fact, the features extracted by machine learning techniques are 
			in the form of arrays of numbers, so to compute the prototype of the image in this form it's enough to take the weighted average of the vectors. The weights should be taken according to the perceived typicality 
			of the category example, which is the average of the measures collected with the survey.

		\subsection{After the alternative data collection method}
